A comparative analysis of AquaMaps and IUCN species ranges

### 2015-12-09 ms_outline.Rmd
tweaking the intro with some IUCN numbers

The IUCN Red List of Threatened Species has assessed **X** number of marine species, but only (**Y**) have associated spatial information. AquaMaps has developed range maps for over 22,800 species. There are only 2,100 species that have maps in both datasets. This gap in overlapping species between these two datasets further highlights the need for understanding each of these datasets. Both IUCN and AquaMaps have gaps in marine species information and a significant portion of available data may be overlooked if limited to just one of these datasets.

@@

The maps provided by the IUCN for each assessed species are created by one or a few experts on that species. There are general guidelines to how the map should be created. Specifically, the final mapped polygons are meant to indicate that a species *probably only occurs within the polygon* but that the species *is not* evenly distributed everywhere within the polygon. The guidelines vary slightly for each type of species (terrestrial, freshwater, marine). These maps are dependent on records of observations from databases such as GBIF.

>>>>

The IUCN Red List of Threatened Species includes more than 19,000 assessed marine species, 
<!--define what "assessed" means? include DD? keeping those in for now--> but only **4463** <!--11975 maps in those shapefiles, but fewer than 4500 correspond to assessed marine species... and only 2500 of those overall correpond to AquaMaps species--> of these have associated spatial information. AquaMaps has developed range maps for over 22,800 species. Only 2,100 species have been mapped in both datasets. This gap in overlapping species between these two datasets further highlights the need for understanding each of these datasets. Both IUCN and AquaMaps have gaps in marine species information and a significant portion of available data may be overlooked if limited to just one of these datasets.

@@

The maps provided by the IUCN for each assessed species are created by one or more experts on that species. There are general guidelines to how the map should be created. Specifically, the final mapped polygons are meant to indicate that a species *probably only occurs within the polygon* but are *not* meant to indicate that the species is evenly distributed everywhere within the polygon. The guidelines vary slightly for each type of species (terrestrial, freshwater, marine). These maps are typically dependent on observation records from databases such as GBIF.
